Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-30 latex/afm-cs-main.tex
typo.
Update abstract. Change fig 8 to show 8hz for raster.

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim
  to reduce the time to acquire an image by reducing the number of
  measurements needed while still maintaining image quality. The approach consists of two components: data acquisition and image reconstruction. While the underlying idea is straightforward, practical implementation of a working scheme involves solving a variety of non-trivial problems. In this
  paper, we describe one such hardware implementation and demonstration based on the use of collections of short scans
  known as $\mu$--paths. Using a commercial AFM, we acquire data on a
  grating sample. Reconstructions are made from these data using
  a new variant of basis pursuit, Basis Pursuit with Vertical
  Variation, that is designed to reduce artifacts arising from
  the sampling pattern. The quality of the resulting images is
  compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio
  and the structured similarity index metric and a new metric we call
  the relative damage index. These images are compared (across a range of scan speeds)
  to both standard raster
  scans as well as to simple subline sampling where only a subset of the
  rows of the image are acquired (followed by reconstruction).
  These experiments show that at low sampling densities and slow scan rates,
  $\mu$-path scanning achieves better image quality than subline sampling.
  Conversely, for faster scan rates, subline sampling achieves better image quality
  in less time, though at a penalty in the damage index.
  % These experiments demonstrate that at slow scan
  % rates, the $\mu-$path scheme produces similar image quality with
  % significantly less sampling (and thus less tip-sample interaction)
  % and that at high rates, the undersampling scheme produces higher
  % quality images than raster scanning.
\end{abstract}

@@

Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
the different sub-sampling schemes over a full raster scan with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
This speed advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 3~Hz, the 64 line scan is faster than the 12.5\% CS scan and
the 128 line scan is faster than the 25\% CS scan. 
In general, the artifacts of the CS reconstructions are different than the interpolated raster scans.
CS appears to preserve the edges of the holes better than sub-line sampling while sub-line sampling has less noise in the flat areas of the specimen.

@@

We then experimentally demonstrated $\mu$-path sub-sampling
and compared the resulting images to both full raster scans
and course raster scans paired with reconstruction.
The main conclusion of this comparison is that with $\mu$-paths, we
can acquire images faster yet with less specimen damage than is
possible while raster scanning a full image and that for slow scan rates,
$\mu$-path scanning achieves better images in less time than subline sampling.
On the other hand, for faster scan rates, reconstructing a coarse raster scan makes more sense.
This is notable, since a coarse raster scan with reconstruction is considerably
easier to implement, both on the hardware side as well as the post-processing side. 
It remains to be seen if this conclusion holds for a wide range of instruments.

>>>>

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim
  to reduce the time to acquire an image by reducing the number of
  measurements needed while still maintaining image quality. The approach consists of two components: data acquisition and image reconstruction. While the underlying idea is straightforward, practical implementation of a working scheme involves solving a variety of non-trivial problems. In this
  paper, we describe one such hardware implementation and demonstration based on the use of collections of short scans
  known as $\mu$--paths. Using a commercial AFM, we acquire data on a
  grating sample. Reconstructions are made from these data using
  a new variant of basis pursuit, Basis Pursuit with Vertical
  Variation, that is designed to reduce artifacts arising from
  the sampling pattern. The quality of the resulting images is
  compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio
  and the structured similarity index metric and a new metric we call
  the relative damage index. These images are compared (across a range of scan speeds)
  to both standard raster
  scans as well as to simple subline sampling where only a subset of the
  rows of the image are acquired (followed by reconstruction).
  These experiments show that at low sampling densities and slow scan rates,
  $\mu$-path scanning achieves better image quality in less time than subline sampling.
  Conversely, for faster scan rates and higher densities, subline sampling
  achieves better image quality in less time.
  % These experiments demonstrate that at slow scan
  % rates, the $\mu-$path scheme produces similar image quality with
  % significantly less sampling (and thus less tip-sample interaction)
  % and that at high rates, the undersampling scheme produces higher
  % quality images than raster scanning.
\end{abstract}

@@

Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
the different sub-sampling schemes over a full raster scan with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the 1~Hz 64 line raster scan.
This speed advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 3~Hz, the 64 line scan is faster than the 12.5\% CS scan and
the 128 line scan is faster than the 25\% CS scan. 
In general, the artifacts of the CS reconstructions are different than the interpolated raster scans.
CS appears to preserve the edges of the holes better than sub-line sampling while sub-line sampling has less noise in the flat areas of the specimen.

@@

We then experimentally demonstrated $\mu$-path sub-sampling
and compared the resulting images to both full raster scans
and course raster scans paired with reconstruction.
The main conclusion of this comparison is that with $\mu$-paths, we
can acquire images faster yet with less specimen damage than is
possible while raster scanning a full image and that for slow scan rates,
$\mu$-path scanning achieves better images in less time than subline sampling.
On the other hand, for faster scan rates (and especially with higher sampling densities), reconstructing a coarse raster scan makes more sense.
This is notable, since a coarse raster scan with reconstruction is considerably
easier to implement, both on the hardware side as well as the post-processing side. 
It remains to be seen if this conclusion holds for a wide range of instruments and specimens.
